l

### 2023-10-03 resume/Resume.tex
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@ce1015d2bef32d302bda5e7484df4ff634635750 🚀

%\section{\textsc{Research Interests}}
%\begin{itemize}
%\item AI: Mechanistic Interpretability, Heuristic Arguments, Compact Proofs, Löb's Theorem
%\item Security \& Engineering: Formal Verification, Cryptography, Bugs \& CI Infrastructure
%\item Programming Languages: Type Theory, Performance, Proof Engines \& Automation
%%
%%\item Mechanistic Interpretability: Heuristic Arguments, Compact Proofs, Type Theory
%%\item Security Engineering: Formal Verification, Cryptography, Performance Engineering
%%\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
%%%\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
%\end{itemize}
\section{\textsc{About Me}}
\vspace*{-0.25cm}
I'm a programming languages research scientist transitioning into ML and alignment.
I have a working knowledge of around two dozen programming languages, and expertise in a handful (Coq ($\approx$1M+ loc), Python ($\approx$50k loc), Agda ($\approx$50k loc), others).
I spent my PhD on low-level cryptographic code generation, proof automation, performance engineering, and infrastructure around debugging and CI.
My current project is in mechanistic interpretability, heuristic arguments, and compact proofs.
I'm excited about what scalable performant automation can make possible.

>>>>

%\section{\textsc{Research Interests}}
%\begin{itemize}
%\item AI: Mechanistic Interpretability, Heuristic Arguments, Compact Proofs, Löb's Theorem
%\item Security \& Engineering: Formal Verification, Cryptography, Bugs \& CI Infrastructure
%\item Programming Languages: Type Theory, Performance, Proof Engines \& Automation
%%
%%\item Mechanistic Interpretability: Heuristic Arguments, Compact Proofs, Type Theory
%%\item Security Engineering: Formal Verification, Cryptography, Performance Engineering
%%\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
%%%\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
%\end{itemize}
\section{\textsc{About Me}}
\vspace*{-0.25cm}
Research scientist with extensive experience in proofs and formal verification transitioning to AI \& ML.
Currently researching mechanistic interpretability, heuristic arguments, and compact proofs.
Programming language polyglot, with working knowledge of around two dozen programming languages, and expertise in a handful (Coq (1M+ loc), Python (40k+ loc), Agda (40k+ loc), others).
I spent the years of my PhD on low-level cryptographic code generation, automation, performance engineering, and infrastructure around debugging and CI.
